\section*{Preface}
\addcontentsline{toc}{section}{Preface}
This collection of papers is the result of our 9th semester work, as software engineers, in Human Computer Interaction, at the Department of Computer Science at Aalborg University.

The theme of our project is cross-device interaction between mobile devices and large displays. Here we present two papers. 

The first paper is a literature review over the current state of the art in regards cross-device natural user interaction for mobile devices and large displays. In this work we analytically summarized relevant research outlining the current field and potentially identifying knowledge gaps. 

The second paper presents a research experiment regarding four different cross-device natural user interaction techniques. Here we explore the techniques based on success rate, efficiency, accuracy and ease of use. We then present our result and discuss their implications.

The reader is expected to have knowledge equivalent to what is expected for a 6th semester student in computer science.

A CD containing the source code of the developed systems is supplied together with this report. The CD also contains a digital copy of this report as well as appendices with e.g. interview transcriptions. Additionally, it contains all logged numbers used for the quantitative analysis, enclosed as database exports.

We would like to thank Jeni Paay, Associate Professor at Aalborg University, for providing ongoing feedback and guidance throughout the project