% !TEX root = ../paper.tex
\begin{abstract}
<<<<<<< HEAD
In recent years, research into cross-device interaction techniques has increased. Much of this research focuses on interaction between mobile devices and large displays. We contribute to this body of knowledge with an empirical comparison of four different push techniques - \pinch, \swipe, \throw,  and \tilt for interaction between mobile devices and large displays. We report on Efficiency, Success rate and Accuracy. We also present the ease of use of techniques as perceived by users. We show that \swipe was the most effective in terms of efficiency and accuracy, furthermore it gathered the highest score, in regards to ease of use, by users. Participants also reported that \pinch was the most fun to use. We also found that proportionally larger target \todo{write what we found in comparison grid size + techniqes.}
=======
In recent years, research into cross-device interaction techniques has increased. Much of this research focuses on interaction between hand-held devices and large displays. We contribute to this body of knowledge with an empirical comparison of four different push techniques - \swipe, \throw, \pinch and \tilt for interaction between mobile phones and large displays. We report on time to hit target, target hit success, and hit distance from target. We also report on ease of use of techniques as perceived by users. We show that \swipe was the most effective in terms of efficiency and accuracy and was reported by users as the most satisfying. Most participants also reported that \pinch was the most fun to use. We also found that proportionally larger target \todo{write what we found in comparison grid size + techniqes.}
>>>>>>> 54468705cdafdc7cd476110c55788a3b76ecc1ff
\end{abstract}
