% !TEX root = ../paper.tex
\section{Conclusion}
We have presented 4 different interaction techniques and compared them to each other, in order to determine their strengths and weaknesses.
We also examined the effect of having larger vs. smaller targets on the screen, in order to simulate the need for either less or increased precision in applications and see what kind of effects it had on time per target and hit ratio per target. 

We discovered that out of the four techniques, \swipe, \throw, \tilt and \pinch, \swipe was the most precise and effective technique. We also showed that \swipe was the technique users had the most positive attitude towards. 
\swipe could be used to create more formal applications, were the need for effectiveness and precision are critical to the application, such as a presentation tool or professional data exchange tool. 

We demonstrated that \pinch was one of the most interesting techniques, but was also one of the more complex techniques to learn and master. 
Depending on the context, this technique could be used to create a more engaging and entertaining application, if it was designed around the assumption that users would have regular interaction with it and ample time to learn and master it.
A game could possibly utilize this technique to great effect. 

We also uncovered that the need for precision comes at a great cost for  effectiveness. 
If possible, developers should try to side-step this need by either making targets large or error friendly.
This could be achieved by developing methods of accurately determining the users intended target.
"Snapping" behavior could also be implemented to great effect, where if the users managed to hover close the target, the pointer would snap onto the target, decreasing the need for accuracy. 