\textit{\textbf{Literature Review:}} In this paper we present a state of the art discussing the literature from two emerging and relatively new areas of the HCI field, namely cross-device interaction and natural user interaction. 
Papers from these two areas are reviewed and categorized into 5 themes: Interacting with large displays, Interacting with public displays, Natural user interactions, Cross-device interactions, and Public space and cross-device natural user interactions. We present an overview of each theme and analytically outline them, furthermore we discuss their connection presenting their overlapping areas.  Our finding indicate a concentration of research in natural user interaction, and cross-device interaction, but limited work in cross-device natural user interaction, suggesting a gap in HCI knowledge worth investigating.\\

\textit{\textbf{Research Paper:}} In recent years, research into cross-device interaction techniques has increased. Much of this research focuses on interaction between mobile devices and large displays. We contribute to this body of knowledge with an empirical comparison of four different push techniques - \textit{Pinch}, \textit{Swipe}, \textit{Throw},  and \textit{Tilt} for interaction between mobile devices and large displays. We report on Efficiency, Success rate and Accuracy. We also present the ease of use of techniques as perceived by users. We show that \textit{Swipe} was the most effective in terms of success rate, efficiency and accuracy. Furthermore it gathered the highest score, in regards to ease of use, by users. Participants also reported that \textit{Pinch} was the most fun to use.