% !TEX root = ../literature.tex
\subsection{Cross-Device Interaction}
Interaction was understood, usually, as single user using a single device, this was almost always a desktop computer\cite{Levin:2014}. We have moved from this protocol into the more complex world of cross device interaction, as such it is important to give definition of this phenomenon.\\

\emph{"Cross-device interaction is the type of interaction, where human users interact with multiple separate input and output devices, where input devices will be used to manipulate content on output devices within a perceived interaction space with immediate and explicit feedback."} \cite{Scharf:2013}.\\

Rikimoto presents an early envisionment of this idea. In his work the technique he proposed was a Prick-and-Drop technique, he explains that "Pick-and-Drop allows a user to pick up an object on a display and drop it on another display as if he/she were manipulating a physical object." \cite{Rekimoto:1997}. The author discusses how, even though from a functional point of view, the technique does not differ from a traditional remote copy command, the added extra layer of physicalness makes a difference for the user. \emph{"understanding that we are living in a fusion of physical (real) and virtual (computer) worlds. Each has its own advantages and disadvantages. Pick-and-Drop, for example, adds physicalness to user interfaces, because we feel that traditional data transfer methods are too virtual and hard to learn due to their lack of physical aspects"} \cite{Rekimoto:1997} remarks the writer.\\
Perhaps one of the earliest working systems illustrating CDI is by Myers et al.
\cite{Myers:2001} one of the application realized within their \emph{Pebbles project} is SlideShow Commanded that utilized Personal Devices Assistants (PDA) to control a PowerPoint presentation running on other computer or laptop.
It was possible not just moving between slides, but also scribbling and writing on the PDA slides, while annotations are shown on the presentation for the audience.\\

Hamilton and Wigdor have a more modern reading on this, they wanted to see how the users would utilize a group of tablets with cross-device capabilities. For this task they crafted\emph{ "Conductor, a prototype system that combines a set of interaction techniques designed to enable single user, cross-device applications, manage cross-device relationships, and enable easy functionality chaining."} \cite{Hamilton:2014}.\\

Radle et. al continued with the multi-tablet cross-device interaction, however their focus shift to the competing interaction techniques. They define three categories: \begin{enumerate}
	\item Synchronous gestures
	\item Spatially-agnostic interactions
	\item Spatially-aware interactions. 
\end{enumerate} They found \emph{"the results indicate that spatially-aware techniques are preferred by users and can decrease mental demand, effort, and frustration, but only when they are designed with great care."} \cite{Radle:2015}.\\

Cross interaction between the same type of device are not the only one. Schmidt et al. propose a cross-device interaction style for mobiles and surfaces. The researchers point out that \emph{"natural forms of interaction have evolved for personal devices that we carry with us (mobiles) as well as for shared interactive displays around us (surfaces) but interaction across the two remains cumbersome in practice"} \cite{Schmidt:2012}; so in order to overcome this they propose to use mobiles as tangible input on the surface in a stylus like fashion.\\

Boring et. al. takes cross-device interaction with mobiles and large displays. Their idea is to combine the largescale visual output and the mobile phone as an input, to enable a channel of communication which is bidirectional with the large public display. To do this they \emph{"propose and compare three different interaction techniques (Scroll, Tilt and Move) for continuous control of a pointer located on a remote display using a mobile phone"} \cite{Boring:2009}.\\
Skov et al. \cite{Skov:2015} illustrate six different cross-device interaction techniques for the case of card playing in \emph{Investigating Cross-Device Interaction techniques}.
A player can see their own cards on their phone and use three different techniques for playing a card from the handheld to the tablet, which is placed on a table.
In the other direction, i.e. when drawing a card, the player also has three techniques to choose from.
The usability study aims to quantitatively evaluate each of the techniques and showed that there is a difference in time and number of errors between the techniques. \\

The current paragraph exemplifies that designing a solution for cross-device interaction can be complex, as such to understand  unique properties and challenges of the domain is a must. The early literature focuses on interaction support. Gradually this evolves to understanding the interaction process itself in different device environment i.e. large display and hand-held device, and multiple hand-held device.With the body of knowledge on cross-device, and natural interactions as part of large display, a logical step is to look and ask if researchers have tried to combine CDI and NUI in public spaces with large displays.
