% !TEX root = ../literature.tex
\section{State of the art of interacting with large displays}
We present an overview of research in interaction techniques for cross device interaction between hand-held devices and large display, with an emphasis on natural user interaction.\\

%talk about an interest in developing technology for public spaces - I also think that you did search on the key word public space - so it should be listed with the other search topics
Our initial search was based on an interest for developing walk-up and use large display technologies for public spaces.We looked at MobileHCI, CHI and ITS conferences in the last 5 years, based on the resent research, presented in those conferences, we selected areas that we thought intersect between research needs and our interests. Those selected were: Cross-device Interaction, Large Displays, Multi-device Interaction, Natural User Interface, Proxemics, Public Space, Social Interaction, Tabletop Interaction, and Tangible Interaction. We used these topics for further inquiry publications within those areas. For the purpose of that we used in ACM DigitalLibrary, SpringerLink and Microsoft Research. From this search and the set of papers found during brainstorming, we kept a total of 56 papers.\\ %% Should we add google?

Based on one of our ideas and the literature we had found we chose to conduct research on interaction techniques for cross-device-interaction between hand held devices and large displays and hereby foregoing Public Space, Social Interaction, Tabletop Interaction, and Tangible Interaction as part of our continued research.
%I'm not sure that all our papers follow this criteria.%To narrow down our focus we selected papers that matched a set of strict criteria: (1) The paper should contain one or more interaction techniques.
%Jeni didn't like this % (2) It is important that the techniques are evaluated using either interviews, surveys, field studies or any other research method.\\

We chose to narrow the search down by focusing on interaction techniques, cross-device interaction, large displays, and technology that could be used to accomplish our idea. We added a strict criteria, that the paper should contain one or more interaction technique. This resulted in an additional 21 papers.\\ %%accomplish... not sure if that is a good choice of word.

With a total of 77 papers, we settle on a research idea and choose to sort away the papers that were unrelated to the research idea and its application.
%%#1 Notice that the above is for the continued search only, we still have papers from public space. Can we define that more clearly?
The final set contained 34 literature sources which we further examined, by writing a short summary for each paper which included ``title, author's thesis (aim of paper), objectives (goals, summaries), methodologies used, findings, conclusion, and keywords''. 
Using applied thematic analysis different themes were induced on the summaries, which we later categorized into 5 themes: interaction with large displays, interaction with public displays, natural user interactions, cross-device interactions, cross-device natural user interactions.\\
%%#2  how can we say public disply if we left the idea of researching for public space
The identified themes and the specific papers correlated to them are presented in \Cref{tab:themes}, with full citations in the references section of this paper. 

\todo[inline]{Check Capital letters in figure. Should each topic end on s (plural)?. Cross-device natural user interactions or Cross-device interaction and natural user interactions? - we use CDINUI in other places  }
\begin{table}[h!]
\centering
\begin{tabular}{@{}p{5cm}p{3cm}@{}}
\toprule[2pt]
Theme & Paper \\\midrule[2pt] 
Interacting with Large displays      & \cite{Weiser:1991} \cite{Hinrichs:2013:IPD:2478559.2478965} \cite{Wellner:1993} \cite{Buxton:2000} \\\midrule%    [1] [3] [32][33] \\
Interacting with Public displays      & \cite{Brignull:2003} \cite{Ojala:2012:MIP:2225044.2225065} \cite{Schieck:2012:AEM:2393132.2393141} \cite{Boring:2013} \cite{Jacucci:2010} \cite{Ren:2013} \cite{Lucero:2012} \cite{Valkanova:2014} \cite{Huang:2003} \\\midrule%    [4] [5] [6] [7] [8] [10] [11] [12] [34] \\
Natural user interactions      & \cite{Jain:2011}\cite{Keefe:2001} \cite{Vogel:2005} \cite{Aigner:2012} \cite{Karam:2005} \cite{Walter:2014} \cite{Wigdor:2011} \cite{Wilson:2010} \cite{KinectFiction:2010} \cite{KinnectPower:2012} \\\midrule% [9] [13] [14] [15] [16] [17] [18]  [30] [31] \\
Cross-device interactions      & \cite{Levin:2014}\cite{Scharf:2013} \cite{Rekimoto:1997} \cite{Hamilton:2014} \cite{Radle:2015} \cite{Schmidt:2012} \cite{Boring:2009} \\\midrule% [20] [21] [22] [23] [24] [25] \\
Cross-device natural user interactions      & \cite{Marquardt:2011} \cite{Marquardt:2012} \cite{Seifert:2012} \cite{Bragton:2011} \\%     [26] [27] [28] [29] \\
\bottomrule
\end{tabular}
\caption{Themes of the reviewed papers.}
\label{tab:themes}
\end{table}

% subsections
\input{docs/largedisplays}
\input{docs/publicdisplays}
\input{docs/nui}
\input{docs/cdi}
\input{docs/public}
\input{docs/cdinui}
\input{docs/discussion}